Medical Training for Abortion Procedures and Physician Provision of Abortions in the United States

### 2016-04-30 paper.tex
Correctly use \footnote{} in paper; put blurb on use of references

% Enablers, barriers, consequences
Creating, maintaining, and teaching such a family planning and abortion program in medical residency is not as simple as following the mandate. Within OB/GYN residency programs that include abortion training, there are a number of factors that enable the training and others that are barriers to effective training.
Enablers of training, identified in a qualitative survey of participants in OB/GYN residency in New York City (NYC), include: program/facility location, access to high-capacity services, faculty commitment to training, Ryan Program \autocite{bixby_center_for_global_reproductive_health_education_????} \autocite{bixby_center_for_global_reproductive_health_home_????} \autocite{steinauer_benefits_2013} support, and interest of residents. \autocite[pg. 240--2]{guiahi_enablers_2013}
Identified barriers to training include: poor continuity in leadership, conflict between leaders, lack of exposure to second-trimester abortion, difficulty acquiring mifepristone, \note{One of the drugs used to induce medical abortion, usually with misoprostol.} burden and incompleteness of opt-in training, and antiabortion values of leadership/staff. \autocite[pg. 242]{guiahi_enablers_2013}
The author emphasizes that these results are not generalizable due to the high-density, urban nature of the survey and the ``politically favorable environment'' experienced in NYC. \autocite[pg. 243]{guiahi_enablers_2013}
In other areas that are less accepting of providing abortion care, it is likely that the enabling factors will be less present and the barrier factors may be more significant or other barriers may be present.

>>>>

% Enablers, barriers, consequences
Creating, maintaining, and teaching such a family planning and abortion program in medical residency is not as simple as following the mandate. Within OB/GYN residency programs that include abortion training, there are a number of factors that enable the training and others that are barriers to effective training.
Enablers of training, identified in a qualitative survey of participants in OB/GYN residency in New York City (NYC), include: program/facility location, access to high-capacity services, faculty commitment to training, Ryan Program \autocite{bixby_center_for_global_reproductive_health_education_????} \autocite{bixby_center_for_global_reproductive_health_home_????} \autocite{steinauer_benefits_2013} support, and interest of residents. \autocite[pg. 240--2]{guiahi_enablers_2013}
Identified barriers to training include: poor continuity in leadership, conflict between leaders, lack of exposure to second-trimester abortion, difficulty acquiring mifepristone, \footnote{One of the drugs used to induce medical abortion, usually with misoprostol.} burden and incompleteness of opt-in training, and antiabortion values of leadership/staff. \autocite[pg. 242]{guiahi_enablers_2013}
The author emphasizes that these results are not generalizable due to the high-density, urban nature of the survey and the ``politically favorable environment'' experienced in NYC. \autocite[pg. 243]{guiahi_enablers_2013}
In other areas that are less accepting of providing abortion care, it is likely that the enabling factors will be less present and the barrier factors may be more significant or other barriers may be present.
